Check Regression Assumptions of Pilot Data
=================================================
This report graphs and runs tests to check the assumptions of the multiple regression.

<!--  Set the working directory to the repository's base directory; this assumes the report is nested inside of only one directory.-->
```{r, echo=TRUE, message=F} 
opts_knit$set(root.dir='../')  #Don't combine this call with any other chunk -especially one that uses file paths.
```

<!-- Set the report-wide options, and point to the external code file. -->
```{r set_options, echo=TRUE}
require(knitr)
opts_chunk$set(
    results='show', 
    comment = NA, 
    tidy = FALSE,
    fig.width = 5.5, 
    fig.height = 4, 
    out.width = "600px", #This affects only the markdown, not the underlying png file.  The height will be scaled appropriately.
    fig.path = 'figure_rmd/',     
    dev = "png",
#     dev = "pdf",
    dpi = 400
)
echoChunks <- FALSE
options(width=120) #So the output is 50% wider than the default.
read_chunk("./Analysis/PilotRegression.R") 
```
<!-- Load the packages.  Suppress the output when loading packages. --> 
```{r LoadPackages, echo=echoChunks, message=FALSE}
```

<!-- Load any Global functions and variables declared in the R file.  Suppress the output. --> 
```{r DeclareGlobals, echo=echoChunks, results='show', message=FALSE}
```

<!-- Declare any global functions specific to a Rmd output.  Suppress the output. --> 
```{r, echo=echoChunks, message=FALSE}
```

<!-- Load the datasets.   -->
```{r LoadDatasets, echo=echoChunks, results='show', message=FALSE}
```

<!-- Tweak the datasets.   -->
```{r TweakDatasets, echo=echoChunks, results='show', message=FALSE}
```

## 1. Gender_PeerRatedDefensiveEgotism_PeerRatedBullying
*Gender, defensive egotism, and bullying.* We regressed peer-rated bullying (Column B in the Excel file, Will) onto gender (Column D), peer-rated defensive egotism (Column F), and the interaction term (Column G). 

```{r Gender_PeerRatedDefensiveEgotism_PeerRatedBullying, echo=echoChunks, results='show', message=TRUE}
```

## 2. Gender_PeerRatedDefensiveEgotism_PeerRatedDefensiveEgotism
*Gender, defensive egotism, and assists or supports the bully.* When we re-ran the analyses above with peer-rated assists or supports the bully as the dependent variable (Column H, Will) (rather than peer-rated bullying), the pattern was almost identical to that in Figure 1. 

```{r Gender_PeerRatedDefensiveEgotism_PeerRatedDefensiveEgotism, echo=echoChunks, results='show', message=TRUE}
```

## 3. Gender_TeacherRatedDefensiveEgotism_TeacherRatedSocialAggression
*Gender, defensive egotism and social aggression.* We regressed teacher-rated social aggression (Column I, Will) onto gender (Column D), teacher-rated defensive egotism (Column K), and the interaction term (Column L), 

```{r Gender_TeacherRatedDefensiveEgotism_TeacherRatedSocialAggression, echo=echoChunks, results='show', message=TRUE}
```

## 4. Gender_PeerRatedSelfEsteem_PeerRatedVictimOfBullying
*Gender, self-esteem and victim of bullying.* We regressed peer-rated victim of bullying (Column M) onto gender (Column D), peer-rated self-esteem (Column O), and the interaction term (Column P) 

```{r Gender_PeerRatedSelfEsteem_PeerRatedVictimOfBullying, echo=echoChunks, results='show', message=TRUE}
```

## 5. Gender_PeerRatedSelfEsteem_PeerRatedDefendsTheVictim
*Gender, self-esteem and defends the victim of bullying*. We regressed peer-rated defends the victim (Column Q) onto gender (Column D), peer-rated self-esteem (Column O), and the interaction term (Column P) 

```{r Gender_PeerRatedSelfEsteem_PeerRatedDefendsTheVictim, echo=echoChunks, results='show', message=TRUE}
```


For the sake of documentation and reproducibility, the current report was build on a system using the following software.

```{r session_info, echo=FALSE}
cat("Report created by", Sys.info()["user"], "at", strftime(Sys.time(), "%F, %T %z"))
sessionInfo()
```
